Binary companions of red giant stars in \apogee\ \DR: \\ Search method and catalog of $>$4,500 systems

### 2018-03-08 paper/1-catalog/twoface-catalog.tex
some tweaks

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
a few qualitatively different solutions.
For these stars, one or a few more RV measurements would likely lead to
uniquely-determined orbital parameters; These stars are prime candidates for
follow-up efforts.
As examples of such cases, we include an additional catalog of systems that have
effectively bimodal posterior samplings in orbital period.
We identify these systems using $k$-means clustering (\citealt{Lloyd:1982}) of
the posterior samples in period.
In detail, for all stars in the high-$K$ sample, we compute $\ln P$ for all
period samples, then use $k$-means clustering with $k=2$ as implemented in the
\texttt{scikit-learn} package (\citealt{Pedregosa:2011}) to identify two
clusters of samples.
We initialize the cluster positions at either end of the range of possible
periods.
For each cluster, we then ask whether the samples assigned to that cluster are
unimodal (\eqname~\ref{eq:unimodal}).
If the samples in each respective cluster are unimodal, we call the sampling
``bimodal''; \nbimodal\ systems are identified as bimodal.

@@

\tablename~\ref{tbl:highK-bimodal} contains a list of all \apogee\ targets with
bimodal samplings identified in this way.
The table contains two rows for each source, with the period, eccentricity, and
velocity semi-amplitude values from the MAP sample from each period mode.

@@

\todo{We could instead select stars with log(Pmax) - log(Pmin) < 1, or some other metric to select things that have constrained periods but are multimodal}

@@

@@

\todo{Companion mass and mass-ratio distribution for stars with Ness / Martig masses}

\todo{Interesting companions w/ large M2min, WD/NS/BH companions?}

\todo{Plot: M1 vs. M2min}

\todo{Plot: M2min vs. a2sini}

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=0.7\textwidth]{mass}
\end{center}
\caption{%
TODO
\label{fig:mass}
}
\end{figure}

\subsection{Evidence for tidal circularization}

>>>>

We have visually inspected the inferred orbits for all systems in this sample
and have flagged systems with questionable or invalid fits.
The value of the flag is: 0, when the orbits look reasonable, 1, when the orbits
look reasonable but the value of the inferred excess variance is large, and 2,
when the orbits are clearly poor fits.
Many of the stars flagged as ``2'' look like they may be triple systems, as they
tend to have radial velocity variations over two distinct timescales that are
never well-fit by a single Keplerian orbit.
This flag is included in the catalog (\tablename~\ref{tbl:highK-unimodal}) as
the column \texttt{clean\_flag}; To select a clean sample of companions that
have been successfully vetted by-eye, select only stars with
\texttt{clean\_flag == 0}.

@@

A subset of the high-$K$ sample (\sectionname~\ref{sec:catalog-confident}) have
multimodal posterior distributions over orbital parameters that are limited to
a few qualitatively different solutions.
For these stars, one or a few more RV measurements would likely lead to
uniquely-determined orbital parameters; These stars are prime candidates for
follow-up efforts.
As examples of such cases, we include an additional catalog of systems that have
effectively bimodal posterior samplings in orbital period.
We identify these systems using $k$-means clustering (\citealt{Lloyd:1982}) of
the posterior samples in period.
In detail, for all stars in the high-$K$ sample, we compute $\ln P$ for all
period samples, then use $k$-means clustering with $k=2$ as implemented in the
\texttt{scikit-learn} package (\citealt{Pedregosa:2011}) to identify two
clusters of samples.
We initialize the cluster positions at either end of the range of possible
periods.
For each cluster, we then ask whether the samples assigned to that cluster are
unimodal (\eqname~\ref{eq:catalog-unimodal}).
If the samples in each respective cluster are unimodal, we call the sampling
``bimodal''; \nbimodal\ systems are identified as bimodal.

@@

\tablename~\ref{tbl:highK-bimodal} contains a list of all \apogee\ targets with
bimodal samplings identified in this way.
The table contains two rows for each source, with the period, eccentricity, and
velocity semi-amplitude values from the MAP sample from each period mode.
When available, this table also includes an estimate of the primary mass, $M_1$,
from \citet{Ness:2015} and an estimate of the minimum companion mass, $M_{2,
\textrm{min}}$.

We again visually inspect all systems in this sample and assign a flag based on
the apparent quality of the inferred orbits (see
\sectionname~\ref{sec:unimodal}).
Again, to select a clean sample of companions from this catalog that have been
successfully vetted by-eye, select only stars with \texttt{clean\_flag == 0}.

@@

% Note: We could instead select stars with log(Pmax) - log(Pmin) < 1, or some
% other metric to select things that have constrained periods but are
% multimodal. This would get us more stars, but may be harder to interpret...

@@

Here we highlight a few interesting results from visualizing the properties of
companions in the unimodal and bimodal samples defined above (see \sectionname
s~\ref{sec:catalog-unimodal} and \ref{sec:catalog-bimodal}).
In all figures, we only plot companions with inferred orbits that pass our
visual inspection (\texttt{clean\_flag == 0}).
We additionally restrict to stars with $\log g > 2$ to avoid upper RGB stars
that may have coherent oscillations that mimic RV modulations from companions.

@@

Most of the companions we find have minimum masses $M_{2, \textrm{min}} <
1~\Msun$.
\figurename~\ref{fig:mass}, left panel shows primary and companion mass
estimates for systems with unimodal (black markers) and bimodal (blue lines)
period samplings using primary masses from \citet{Ness:2015}.
Upper dashed line shows the $M_{2, \textrm{min}} = M_1$ line, and lower dashed
line shows the Hydrogen-burning limit, $M_{2, \textrm{min}} = 0.08~\msun$.
For the systems with bimodal samplings, we compute the minimum companion mass
for each period mode and connect these estimates with a line.
Three interesting systems are immediately obvious: two systems with bimodal
period samplings in which both period modes put the minimum companion mass below
the Hydrogen-burning limit, and one system in which $M_{2, \textrm{min}} > M_1$.

% Notebook: "Results"
\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{mass}
\end{center}
\caption{%
TODO
\label{fig:mass}
}
\end{figure}

\subsubsection{2M04582049+2232000}
% BD candidate

\subsubsection{2M20130687+2044173}
% BD candidate

\subsubsection{2M01231070+1801407}
% NS/BH candidate

\subsection{Tidal circularization}
